Topic models

### 2021-03-30 manuscript.Rmd
restructure discussion

authornote: |
  This work is supported by a NWO Veni grant (NWO
  grant number VI.Veni.191G.090). Acknowledgement: Lukas Beinhauer contributed
  substantially to the screening of articles. Conflicts of Interest: None.

@@

Despite the abundance of theory *relevant* to emotion regulation in adolescence,
the literature has several limitations.
First, few theories have explicitly addressed adolescence.
This life stage differs qualitatively from both childhood and adulthood [@bariolaChildAdolescentEmotion2011].
It is therefore questionable whether theories focused on different age groups can be generalized to adolescents.
<!--Relatedly, many relevant theories lack an explicit developmental component, which renders them and thus lack a well-substantiated
understanding of developmental processes[see
@bussTheoriesEmotionalDevelopment2019;
@croneUnderstandingAdolescencePeriod2012]. -->
Furthermore, few theories have comprehensively addressed important predictors of development in this life stage,
and none directly guide contemporary research in the field [@bussTheoriesEmotionalDevelopment2019].
Finally, existing theories vary widely in scope:
Some are broad and non-specific; others describe a specific phenomenon in detail,
but lack a broader perspective.
Broad theories can be used to frame a wide variety of research,
and specific theories are more suitable for deductive hypothesis generation.
To combine the strength of both, it would be beneficial to bridge these levels of analysis.
In sum, there is a need for more integrative theory formation,
in order to provide a unified framework that could guide future empirical work.<!--[see @riedigerEmotionRegulationAdolescence2014].
Inductive analysis of the empirical literature may constitute a first step to this end.-->
<!--Such a theory should focus on -->
<!--
Barriola: What is most
* evident from the reviewed studies is that the samples
investigated have been mainly non-clinical, within the
early childhood period of development and have examined
predominantly maternal socialization factors.
* the vast
majority have been restricted to toddlers and young chil-
dren and have only examined the in?uence of maternal,
and not paternal, expression.
Most of the literature has addressed emotion regulation in adult or infant
samples. A smaller, but substantial, portion of the literature has examined
emotion regulation in adolescents.
-->

@@

## Prior narrative reviews

<!--Whereas theory provides a top-down deductive understanding of adolescents' emotion regulation,-->
Literature reviews synthesize inductive insights emerging from the empirical literature.
They can thus shed a light on undertheorized relevant phenomena.
This is especially important given the noted absence of a single overarching theory [see @bussTheoriesEmotionalDevelopment2019].
One recent narrative review, in exploring which factors contribute to adolescents' emotion regulation development, clearly reflected the emphasis on neurocognitive factors and socialization that is evident from the theoretical literature [@riedigerEmotionRegulationAdolescence2014].
Other recent narrative reviews complement the aforementioned theoretical literature to a greater extent [@coe-odessEmergentEmotionsAdolescence2019; @bariolaChildAdolescentEmotion2011].
The right panel of Figure \@ref(fig:figbaseline) visualizes constructs uniquely covered by these narrative reviews,
relative to the preceding theoretical literature.
This illustrates in what respects these reviews reflect existing theory,
and in what respects they complement it.
<!--
Note that the left panel of Figure \@ref(fig:tmnetworks) visually summarizes the correlates of emotion regulation difficulties (labeled: *Dysregulation*) according to our theoretical review.
The left panel of Figure \@ref(fig:tmnetworks) summarizes key constructs covered by the theories reviewed above. 
In the subsequent text mining analysis, we will distinguish the topics covered in this theoretical review visually to highlight unique contributions of our approach.
This allows us to see in what respects the text mining analysis reflects existing theory,
and in what respects it complements it.-->

@@

The present study used a text mining systematic review (TMSR)
to identify relevant phenomena in the literature on adolescent emotion regulation,
and used co-occurrence graphs to map associations among these phenomena.
A systematic literature search was conducted,
and new procedures were developed to analyze the author keywords (Analysis 1) and abstracts (Analysis 2) of the resulting corpus.

The TMSR approach considers term frequency to be indicative of a phenomenon's relevance.
In line with this assumption, the results of both analyses
reflected some of the constructs commonly accepted as relevant in theoretical literature and empirical reviews - particularly those pertaining to neurodevelopment and socialization.
Furthermore, some of the most frequently occurring terms were mental health-related outcomes that involve emotion regulation difficulties [see @aldaoEmotionregulationStrategiesPsychopathology2010].
This validates the notion that adolescent emotion regulation is implicated in a range of mental health problems [@leeAdolescentMentalHealth2014],
and underlines the importance of this area of research.

The analyses of term frequency also identified several novel themes,
which were underrepresented in the theoretical literature and prior systematic reviews.
One such theme pertains to developmental disorders, such as ADHD/CD and autism.
This theme recurred in both analyses, although its constituent terms were ranked more highly in the analysis of author keywords as compared to abstracts.
Another theme revolved around adolescents' physical health (sic), which was also reflected in terms like sleep, sports, and disability status.
There thus appears to be substantial empirical work linking emotion regulation and physical health, although this association is underrepresented in theory.
As with the theme of developmental disorders, terms related to physical health ranked more highly in the keyword analysis than in the abstract analysis.
This might indicate that a broader vocabulary was used to describe physical health in the abstracts.
External stressors were another important theme, reflected in terms like bullying, stress, PTSD, abuse, violence, life events, historic events (e.g., earthquakes, war), parenting stress, and divorce.
Based on a review of the theoretical literature, this indeed appears to be an under-theorized area.
Conceptually, external stressors most closely align with the notion of the exosystem in the bioecological model [@bronfenbrennerBioecologicalModelHuman2007], but have rarely been discussed as such in the theoretical literature.
The impression that external stressors are an undertheorized theme is reinforced by the fact that studies linking adverse life events to adolescent emotion regulation tend to appeal to prior empirical work, but not to a theoretical framework [ @stikkelbroekAdolescentDepressionNegative2016].
Finally, one emergent theme that appears to be underrepresented in existing theory is structural disadvantage.
This theme was reflected in terms like minority status and discrimination, disability status, socio-economic status, adoption status, and sexual diversity. 
The aforementioned developmental disorders are also relevant in this context, as neuroatypical individuals tend to experience social exclusion [@cappadociaBullyingExperiencesChildren2012].
Future theoretical work might address these shortcomings.

The analysis of abstracts identified three additional themes not represented in the analysis of keywords.
The first of these themes revolved around addictive behavior, with indicators *substance use* and *device use*.
The second theme pertained to identity and moral development, two topics with a common root in theory [@lapsleyMoralIdentityDevelopmental2015].
This theme is also reflected by the terms *values* and *personality*. 
Finally, sexual development emerged as a theme. Aside from the high-ranking construct (biological) *sex*, this theme was reflected in the terms *puberty*, *sexual diversity*, and *romantic*.
These insights illustrate how inductive reviews can identify under-theorized areas,
thereby complementing existing theory and narrative reviews.

With regard to term co-occurrence, most phenomena were directly linked with emotion regulation in the keyword analysis,
and with a central axis of emotion regulation and its mental health-related outcomes in the abstract analysis.
The emergence of a "central axis" of dysregulation and mental health-related outcomes
again suggest that these phenomena are consistently studied together.
This makes sense, given the central role of emotion dyregulation in the etiology of diverse mental health problems [@leeAdolescentMentalHealth2014].

Compared to the keyword analysis, the abstract analysis yielded a sparser network,
with fewer selected terms.
This is likely an artifact of the unstructured nature of abstracts,
which introduces greater noise in the analysis.
Thus, fewer terms will exceed the detection threshold.
In line with this interpretation, exploratory analyses indicated that 99% of terms occurred only once in the abstract analysis, compared to only 78% in the keyword analysis.
Despite the sparser network, there was substantial consistency between the terms retained in both networks.
This supports the validity of the findings,
suggesting that automatic keyword extraction from abstracts can identify relevant constructs,
and may be a suitable alternative to author-provided keywords.

Both analyses revealed relatively few interconnections between phenomena,
and many of the frequently occurring terms were absent from the co-occurrence graphs due to a lack of connectivity.
These observations empirically support the prior claim that this literature is somewhat fragmented [@riedigerEmotionRegulationAdolescence2014] and lacks an overarching theoretical framework [@bussTheoriesEmotionalDevelopment2019]. 
The sparseness of both networks explains, in part,
why some of the most prevalent terms based on term document frequency
are absent from the co-occurrence graph (see Figure \@ref(fig:varimps)).
This does not mean that these terms represent unimportant phenomena.
Rather, it suggests that they are not well-integrated in the broader literature on adolescents' emotion regulation.
Such phenomena might be suitable candidates for future research.
Indeed, several of these excluded constructs represent active ongoing areas of research, including research on *fathers* [@vanlissaRoleFathersMothers2019], *identity* [@campbellFriendsEducationIdentity2019], *friendship* and *social support* [@wangBidirectionalEffectsExpressive2020], *autonomy* [@vrolijkLongitudinalLinkagesFather2020a], *sexual risk* [@brownDepressiveSymptomsPredictor2006], and *loneliness* [@spithovenItAllTheir2017].
One recommendation for future research might be to study such important but unembedded constructs
in conjunction with other more well-established constructs,
as such an approach might help fill gaps in existing knowledge.

@@

The results of this inductive approach echoed many of the constructs considered
relevant in the theoretical literature.
This suggests that the text mining method can indeed be used to map relevant themes in the literature.
The present analyses also revealed several themes that have been underrepresented in theories of adolescent emotion regulation,
but nonetheless occur frequently in the empirical literature.
These themes include developmental disorders, physical health, external stressors, structural disadvantage, addictive behavior, identity and moral development, and sexual development.

It is important to identify such under-theorized areas of the literature because
researchers typically rely on theoretical foundations when planning a study.
By providing an overview of phenomena relevant to adolescents' emotion regulation based on an inductive analysis of the empirical literature,
the present study offers guidance regarding potentially relevant topics to consider.
An important direction for future research would be to formalize these inductive insights into a new overarching theory of adolescent emotion regulation.
Going beyond the inductive identification of relevant phenomena,
the next step in theory construction would involve abductive reasoning: the attribution of observations to causal explanatory principles [@haigExploratoryFactorAnalysis2005].
As a starting point for this effort, the co-occurrence graphs presented here could be
used as templates for a nomological network:
a proto-theoretical diagrammatic representation that describes causal relationships between
relevant phenomena [see @alaviAligningTheoryMethodology2018].

Additional insight can be gleaned from the structure of the co-occurrence graphs.
First, both analyses revealed close ties between emotion regulation and mental health-related outcomes.
This is consistent with emotion regulation's putative implication in the etiology of various mental health problems [see @leeAdolescentMentalHealth2014].
It further emphasizes the societal relevance of this field of research.
Both analyses further revealed that most constructs were
directly tied to emotion regulation and mental health,
with few connections among constructs.
This sparse property of the networks echoes the observation by other authors 
that the literature is somewhat fragmented [@riedigerEmotionRegulationAdolescence2014]
and lacks an overarching theoretical framework [@bussTheoriesEmotionalDevelopment2019].
The present study takes a first step toward integrating this diffuse field
by using a relatively comprehensive and objective method, compared to narrative reviews.
An important future direction for research might be to jointly investigate disconnected constructs, as the lack of connections in the graph indicates a potential knowledge vacuum.

@@

@@

It should be noted that this method has disadvantages as well.
The key limitation of the present study is that the text mining techniques used here
are not able to extract *meaning* from the literature in the way a sentient reader would, an cannot substantively interpret connections between constructs.
This limitation is best addressed by considering the output of a text mining analysis as a starting point for further inductive thought or a more in-depth reading of a particular subset of the literature.
Throughout this paper, results are interpreted subjectively.
Readers are encouraged to reflect on these results independently,
and use them as inspiration for future deductive research.

@@

Efforts are currently underway to develop unsupervised algorithms capable of distilling causal links from bodies of scientific abstracts [@anExtractingCausalRelations2019].

@@

To conclude, this paper set out to map the factors associated with adolescents' emotion regulation, based on a systematic review of the literature, and text mining analysis of author keywords and abstracts.
This map covered familiar phenomena that are well-represented in existing theory,
such as socialization and neurocognitive factors,
which speaks to the validity of this approach.
The structure of the map further reinforced the observation of several previous authors
that the empirical literature is somewhat fragmented by subject area [@riedigerEmotionRegulationAdolescence2014] and lacks an overarching theoretical framework [@bussTheoriesEmotionalDevelopment2019].

Importantly, the present results also draw attention to several relevant phenomena that,
although well-represented in the empirical literature,
are under-emphasized in narrative reviews and theory - such as developmental disorders, physical health, external stressors, structural disadvantage, substance use, identity and moral development, and sexual development.
This has several implications for future research.
First, the major themes identified in these inductive analyses are relevant for the design of empirical studies.
Even when such designs are grounded in theory,
they might benefit from additionally considering relevant phenomena as identified in the present study as potential confounders or contributing causes.
Second, the phenomena that appear to exist on the fringes of the existing literature according to the present analyses might be suitable candidates for further study.
These phenomena might represent emerging themes in the literature, for example, as is the case for the role of fathers [see @pleckPaternalInvolvementRevised2004].
Future research might focus on these emerging themes in order to better elucidate the nature of their association with adolescents' emotion regulation.
Moreover, studying these fringe phenomena in conjunction with other more well-established constructs could help embed these important but loosely connected phenomena into the mainstream literature and bridge gaps in existing knowledge.

Finally, several authors have commented on the lack of an overarching theory tailored specifically to adolescent emotion regulation.
The first step in theory construction methodology (TCM) is to identify relevant phenomena [@borsboomTheoryConstructionMethodology2020].
Text mining systematic reviews offer a relatively comprehensive and objective method for identifying such phenomena, because they can evaluate much larger bodies of literature than sentient readers, and are not biased toward pre-existing ideas.
The next step in formal theory construction methodology would be to describe and quantify the nature of the relationship of each phenomenon in relation to adolescent emotion regulation.
The phenomena identified in the present study might thus serve as a starting point for future theory development,
and sensitize empirical researchers to potential confounders in research on adolescents' emotion regulation.

@@

<!-- Here is what I typically tell authors regarding what I need in the conclusion. 
Insert this level 1 heading before it: Conclusion Begin by (briefly) reminding the reader of the topic, the research gap, and how you addressed it. Then go to what you found and its importance.  Be sure to state your findings very clearly. The implications can focus on many aspects of the study, such as the practice implications (briefly). But, for us, the implications also should include a focus on the understanding of adolescence/early adulthood/emerging adulthood and the contribution to that research.  The bulk of the paragraph, though, should be focused on the key findings. Do try to have it be just one strong paragraph.-->

# Acknowledgements
<!-- This is what I need:

As our journal is multidisciplinary and some fields are now moving toward encouraging preregistration, and given that we seek to have authors distinguish between confirmatory and exploratory analyses, we now encourage authors to note whether parts of their study were preregistered. If it is not, then simply ignore. If it is, then please provide the relevant link (URL, DOI or other permanent path to a public, open access repository) and note what was registered (the study design, hypotheses, and target analyses, and so forth).

I will need a statement regarding conflicts of interests. It should have this heading "Conflicts of Interest" and, below it, a sentence reporting your potential conflicts. If you have none, please write a full sentence to this effect: "The authors report no conflict of interests." If you do have conflicts of interests, please report them. For guidance, see the journal's instructions to authors that are posted online. The only part that the journal follows that is different from the online instructions is that we require that the statements be presented in the acknowledgment page rather than in the title page.

I also need a note on funding. [But only if there was funding.]

Just so we are clear, the acknowledgment page should have these items addressed:
Acknowledgment (if you have a general one, otherwise do not use this heading).
Conflicts of Interest
Preregistration (only if relevant)
Funding  (only if relevant)-->

On behalf of all authors, the corresponding author states that there is no conflict of interest
<!--
Informally, much can be gained by revisiting existing relevant theory
and incorporating relevant phenomena as identified in the present analysis.-->
```{r, eval = FALSE}
# These analyses takes very long (~30m); set eval = TRUE to re-run them.
if(run_everything){
  rmarkdown::render("topic_models.Rmd")
}
```

>>>>

@@

Despite the abundance of theory *relevant* to emotion regulation in adolescence,
the literature has several limitations.
First, few theories have explicitly addressed adolescence.
This life stage differs qualitatively from both childhood and adulthood [@bariolaChildAdolescentEmotion2011].
It is therefore questionable whether theories focused on different age groups can be generalized to adolescents.
<!--Relatedly, many relevant theories lack an explicit developmental component, which renders them and thus lack a well-substantiated
understanding of developmental processes[see
@bussTheoriesEmotionalDevelopment2019;
@croneUnderstandingAdolescencePeriod2012]. -->
Furthermore, few theories have comprehensively addressed important predictors of development in this life stage,
and none directly guide contemporary research in the field [@bussTheoriesEmotionalDevelopment2019].
Finally, existing theories vary widely in scope:
Some are broad and non-specific; others describe a specific phenomenon in detail,
but lack a broader perspective.
Broad theories can be used to frame a wide variety of research,
and specific theories are more suitable for deductive hypothesis generation.
To combine the strength of both, it would be beneficial to bridge these levels of analysis.
There is a need for integrative theory formation,
which could provide a unified framework to guide future empirical work.<!--[see @riedigerEmotionRegulationAdolescence2014].
Inductive analysis of the empirical literature may constitute a first step to this end.-->
<!--Such a theory should focus on -->
<!--
Barriola: What is most
* evident from the reviewed studies is that the samples
investigated have been mainly non-clinical, within the
early childhood period of development and have examined
predominantly maternal socialization factors.
* the vast
majority have been restricted to toddlers and young chil-
dren and have only examined the in?uence of maternal,
and not paternal, expression.
Most of the literature has addressed emotion regulation in adult or infant
samples. A smaller, but substantial, portion of the literature has examined
emotion regulation in adolescents.
-->

@@

## Prior Narrative Reviews

<!--Whereas theory provides a top-down deductive understanding of adolescents' emotion regulation,-->
Literature reviews can shed a light on undertheorized relevant phenomena by
synthesizing inductive insights emerging from the empirical literature.
This is especially important given the noted absence of a single overarching theory [see @bussTheoriesEmotionalDevelopment2019].
One recent narrative review, in exploring which factors contribute to adolescents' emotion regulation development, clearly reflected the emphasis on neurocognitive factors and socialization that is evident from the theoretical literature [@riedigerEmotionRegulationAdolescence2014].
Other recent narrative reviews complement the aforementioned theoretical literature to a greater extent [@coe-odessEmergentEmotionsAdolescence2019; @bariolaChildAdolescentEmotion2011].
The right panel of Figure \@ref(fig:figbaseline) visualizes constructs uniquely covered by these narrative reviews,
relative to the preceding theoretical literature.
This illustrates in what respects these reviews reflect existing theory,
and in what respects they complement it.
<!--
Note that the left panel of Figure \@ref(fig:tmnetworks) visually summarizes the correlates of emotion regulation difficulties (labeled: *Dysregulation*) according to our theoretical review.
The left panel of Figure \@ref(fig:tmnetworks) summarizes key constructs covered by the theories reviewed above. 
In the subsequent text mining analysis, we will distinguish the topics covered in this theoretical review visually to highlight unique contributions of our approach.
This allows us to see in what respects the text mining analysis reflects existing theory,
and in what respects it complements it.-->

@@

The present study used a novel method, the text mining systematic review (TMSR),
to identify relevant phenomena in the literature on adolescent emotion regulation,
and used co-occurrence graphs to map associations among these phenomena.
This approach considers term frequency to be indicative of a phenomenon's relevance.
In line with this assumption, the results of both analyses
reflected some of the phenomena broadly considered to be relevant in theoretical literature and empirical reviews - particularly those pertaining to neurodevelopment and socialization.
Other frequently occurring phenomena were mental health-related outcomes that involve emotion regulation difficulties [see @aldaoEmotionregulationStrategiesPsychopathology2010].
This result is consistent with the notion that adolescent emotion regulation is implicated in a range of mental health problems [@leeAdolescentMentalHealth2014],
and underlines the importance of research in this area.

The term frequency analyses also identified several novel themes of relevant phenomena that are underrepresented in the theoretical literature and prior systematic reviews.
One such theme pertains to developmental disorders, such as ADHD/CD and autism.
This theme recurred in both analyses, although its constituent terms were ranked more highly in the analysis of keywords as compared to abstracts.
Another theme revolved around adolescents' physical health (sic), which was also reflected in terms like sleep, sports, and disability status.
This finding indicates that there is substantial empirical work on emotion regulation and physical health, although physical health is underrepresented in theory.
As with the theme of developmental disorders, terms related to physical health ranked more highly in the keyword analysis than in the abstract analysis.
This might indicate that a broader vocabulary was used to describe physical health in the abstracts; a diverse vocabulary increases the difficulty of correctly classifying terms belonging to a theme.
External stressors were another important theme, reflected in terms like bullying, stress, PTSD, abuse, violence, life events, historic events (e.g., earthquakes, war), parenting stress, and divorce.
Based on the review of the theoretical literature, this indeed appears to be an under-theorized area.
Conceptually, external stressors most closely align with the notion of the exosystem in the bioecological model [@bronfenbrennerBioecologicalModelHuman2007], but they have rarely been discussed as such in the theoretical literature.
The impression that external stressors are an undertheorized theme is reinforced by the fact that studies linking adverse life events to adolescent emotion regulation tend to reference mostly prior empirical work, but not a theoretical framework [e.g., @stikkelbroekAdolescentDepressionNegative2016].
Finally, one emergent theme that appears to be underrepresented in existing theory is structural disadvantage.
This theme was reflected in terms like minority status and discrimination, disability status, socio-economic status, adoption status, and sexual diversity. 
The aforementioned developmental disorders are also relevant in this context, as neuroatypical individuals tend to experience social exclusion [@cappadociaBullyingExperiencesChildren2012].
Future theoretical work might address these shortcomings.

The analysis of abstracts identified three additional themes not represented in the analysis of keywords.
The first of these themes revolved around addictive behavior (e.g., substance use and device use).
The second theme pertained to identity and moral development, two topics with a common root in theory [@lapsleyMoralIdentityDevelopmental2015].
This theme is also reflected by the terms values and personality. 
Finally, sexual development emerged as a theme. Aside from the high-ranking construct (biological) sex, this theme was reflected in the terms puberty, sexual diversity, and romantic relationships.
These insights illustrate how inductive reviews can identify under-theorized areas,
thereby complementing existing theory and narrative reviews.

With regard to term co-occurrence, most phenomena were directly linked with emotion regulation in the keyword analysis,
and with a central axis of emotion regulation and its mental health-related outcomes in the abstract analysis.
The emergence of a central axis of dysregulation and mental health-related outcomes
again suggest that these phenomena are consistently studied together.
This makes sense, given the central role of emotion dyregulation in the etiology of diverse mental health problems [@leeAdolescentMentalHealth2014].

Compared to the keyword analysis, the abstract analysis yielded a sparser network,
with fewer selected terms.
This is likely an artifact of the unstructured nature of abstracts,
which introduces greater noise in the analysis.
Thus, fewer terms will exceed the detection threshold.
In line with this interpretation, exploratory analyses indicated that 99% of terms occurred only once in the abstract analysis, compared to only 78% in the keyword analysis.
Despite the sparser network, there was substantial correspondence between the terms retained in both networks.
This supports the validity of the findings,
and suggests that automatic keyword extraction from abstracts can identify relevant constructs,
and may be a suitable alternative to author-provided keywords.

Both co-occurrence networks revealed relatively few interconnections between phenomena,
and several frequently occurring terms were pruned due to a lack of connectivity.
This empirically supports the prior (anecdotal) claim that this literature is somewhat fragmented [@riedigerEmotionRegulationAdolescence2014]. 
The absence of terms from the co-occurrence networks does not mean that these phenomena are unimportant, but rather, that they are not well-integrated in the broader literature on adolescents' emotion regulation.
Several of these unembedded phenomena represent emerging themes in the literature; as is the case for research on fathers [see @pleckPaternalInvolvementRevised2004], identity [@campbellFriendsEducationIdentity2019], friendship and social support [@wangBidirectionalEffectsExpressive2020], autonomy [@vrolijkLongitudinalLinkagesFather2020a], sexual risk [@brownDepressiveSymptomsPredictor2006], and loneliness [@spithovenItAllTheir2017].

@@

This results of this text mining systematic review reflected several familiar phenomena that are well-represented in existing theory.
This has implications for the validity of the method, as it suggests that text mining can indeed be used to map relevant themes in the literature.
The results also revealed relevant phenomena that,
although well-represented in the empirical literature,
are under-emphasized in narrative reviews and theory - phenomena such as developmental disorders, physical health, external stressors, structural disadvantage, substance use, identity and moral development, and sexual development.
This has implication for future empirical research:
In designing a study, researchers typically rely on theoretical foundations - and under-theorized phenomena are at risk of being overlooked.
The present study offers guidance regarding additional relevant phenomena to consider as potential confounders or contributing causes.

The results further revealed that several relevant phenomena were relatively unembedded.
This has implications for future research, as the absence of these phenomena from the co-occurrence networks, and the sparsity of connections in the network, suggest potential knowledge gaps.
Future research might study these unembedded phenomena in conjunction with other more well-established constructs,
in order to bridge gaps in existing knowledge and bring these phenomena into the mainstream literature.

Additional implications arise from the structure of the co-occurrence graphs.
Both analyses revealed close ties between emotion regulation and mental health-related outcomes, which is consistent with the role of emotion regulation in the etiology of mental health problems [see @leeAdolescentMentalHealth2014].
This has implications for the societal relevance of research in this area.
Furthermore, both analyses revealed that most constructs were
directly tied to emotion regulation and mental health,
with few connections among constructs.
These sparse networks validate prior anecdotal claims
that the literature in this field is somewhat fragmented [@riedigerEmotionRegulationAdolescence2014]
and lacks an overarching theoretical framework [@bussTheoriesEmotionalDevelopment2019].
An important implication of this finding is that, indeed, work remains to be done to integrate this diffuse field, and to generate an overarching theory of adolescent emotion regulation.
The first step in theory construction methodology (TCM) is to identify relevant phenomena [@borsboomTheoryConstructionMethodology2020].
The present study takes that first step
by mapping the relevant phenomena in this area of research using a relatively comprehensive and objective method.<!--The relevant phenomena identified in the present study might thus serve as a starting point for future theory development.-->

An important direction for future research would be to formalize these inductive insights into a new overarching theory of adolescent emotion regulation.
According to formal theory construction methodology, the next step would be to describe and quantify the nature of the relationship of each phenomenon in relation to adolescent emotion regulation.
This involves abductive reasoning: the attribution of observations to causal explanatory principles [@haigExploratoryFactorAnalysis2005].
As a starting point for this effort, the co-occurrence graphs presented here could be
used as templates for a nomological network:
a proto-theoretical diagrammatic representation that describes causal relationships between
relevant phenomena [see @alaviAligningTheoryMethodology2018].

@@

## Stengths and Limitations

@@

It should be noted that the present study has limitations as well.
The key disadvantage of the method used is that these text mining techniques
are not able to extract *meaning* from the literature in the way a sentient reader would.
This limitation is best addressed by considering the results as a starting point for inductive reasoning, further deductive research, or a more detailed narrative review on specific sub-topics.

@@

Efforts are currently underway to develop unsupervised algorithms capable of distilling implied causal links from scientific abstracts [@anExtractingCausalRelations2019].

@@

@@

<!-- Begin by (briefly) reminding the reader of the topic
this paper set out to map the factors associated with adolescents' emotion regulation, based on a systematic review of the literature, and text mining analysis of author keywords and abstracts.
-->
There has been a call for the integration of the empirical literature on adolescent emotion regulation.
<!--, the research gap, and how you addressed it.-->
This paper used a text mining systematic review to identify phenomena relevant to adolescents' emotion regulation based on term frequency,
and to map potential associations between phenomena based on term co-occurrence.
<!--Then go to what you found and its importance.  Be sure to state your findings very clearly. -->
The findings reflected several themes commonly featured in theory and narrative reviews,
such associalization and neurocognitive factors,
which suggests that this is a valid method for identifying relevant phenomena.
Importantly, the findings also revealed undertheorized themes,
such as developmental disorders, physical health, external stressors,
structural disadvantage, substance use, identity and moral development, and
sexual development.

<!-- The implications can focus on many aspects of the study, such as the practice implications (briefly).-->

<!--the implications also should include a focus on the understanding of adolescence/early adulthood/emerging adulthood and the contribution to that research.-->
Several of these themes

The findings illustrate how text mining systematic
  reviews, a novel approach, may complement narrative reviews. Future
  theoretical work might integrate these undertheorized themes into
  an overarching framework, and empirical research might consider them as
  promising areas for future research, or as potential confounders in research
  on adolescents' emotion regulation.

# Acknowledgements

## Acknowledgement

Lukas Beinhauer contributed substantially to the screening of articles.

## Conflicts of Interest

The author reports no conflict of interests.

## Preregistration

This study was wholly exploratory. The analyses were not preregistered.
A full historical record of the analyses is available at https://github.com/cjvanlissa/veni_sysrev.

## Funding

This work is supported by a NWO Veni grant (NWO grant number VI.Veni.191G.090),
awarded to the author.

<!--
Informally, much can be gained by revisiting existing relevant theory
and incorporating relevant phenomena as identified in the present analysis.-->
```{r, eval = FALSE}
# These analyses takes very long (~30m); set eval = TRUE to re-run them.
if(run_everything){
  rmarkdown::render("topic_models.Rmd")
}
```
